%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Buddhika Chamith}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{email}{\href{mailto:chamibuddhika@gmail.com}{chamibuddhika@gmail.com}} % Email address

\NewEntry{website}{\href{http://homes.soic.indiana.edu/budkahaw/}{http://homes.soic.indiana.edu/budkahaw/}} % Personal website

\NewEntry{phone}{+1 (317) 909 1713} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Interests}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\Description{I am interested in techniques for monitoring and improving application performance. My specialties are runtime 
binary instrumentation techniques and performance optimizing runtime adaptive applications. My previous work also included work on
large scale data processing.}\vspace{2em} % Goal text

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

% \NewEntry{2013-2016}{Indiana University, Bloomington}

% \Description{\MarginText{MS \\ Computer Science}GPA: 3.85\ \ $\cdotp$\ \ \textit{Minor}: Programming Languages\newline 
% Course Work: Advanced Operating Systems, Advanced Database Systems, Programming Language Implementation, Programming Language Foundations

%------------------------------------------------

\NewEntry{2013-Current}{Indiana University, Bloomington}

\Description{\MarginText{PhD \\ Computer Science}\textit{Minor}: Programming Languages \newline
\textit{Research}: Work on lightweight runtime binary instrumentation techniques.}


%------------------------------------------------

\NewEntry{2013-2016}{Indiana University, Bloomington}

\Description{\MarginText{MS \\ Computer Science}\textit{GPA}: 3.85 \newline
\textit{Selected Course Work}: Advanced Operating Systems, Advanced Database Systems, Programming Language Implementation, Programming Language Foundations, 
Theory of Computing, Machine Learning}

%------------------------------------------------

\NewEntry{2006-2010}{University of Moratuwa, Sri Lanka}

\Description{\MarginText{BSc. \\ Computer Science}\textit{GPA}: 3.91 (out of 4.2) \newline
First Class Honors}


%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------


\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2018 Summer}{Research Intern, \textsc{Science Gateway Research Center}}

\Description{\MarginText{SGRC, Indiana University}\begin{itemize}
  \item Developed Kisseru, a python library for scripting scientific dataflows. Features a 
	lightweight embedded DSL which optimizes the data flow graph and run it locally or on Slurm.
\end{itemize}
}


\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2014--Present}{Research Assistant, \textsc{Indiana University}}

\Description{\MarginText{Center for Research in Extreme Scale Technologies}\begin{itemize}
  \item Developed Liteprof, a lightweight runtime binary instrumentation framework for x86. 
This work is published in PLDI'16 and PLDI'17.
  \item Wrote an algebraic data type serializer for Gibbon research compiler which operates on packed memory representations
of ASTs to yield performance gains. This work was published in ECOOP'17. 
  \item Developed a non‐blocking I/O library and related benchmarks on top of Concurrent Cilk work‐stealing
parallel runtime research prototype. The related work was published in LCPC'15.
  \item Integrated HPX, a C based asynchronous many task runtime as a Haberno CnC backend target. This
work entailed generating HPX C code from the CnC DSL specification using a Python template library.
\end{itemize}
}

%------------------------------------------------

\NewEntry{2013}{Senior Software Engineer, WSO2 Inc}

%------------------------------------------------

\NewEntry{2010--2013}{Software Engineer, \textsc{WSO2 Inc}  --- Colombo}

\Description{\MarginText{WSO2 Inc}\begin{itemize}
  \item Software developer in Business Activity Monitoring team. Was involved in a complete rewrite of the product in order to make it scalable to handle high throughput data ingestion and big data analytics.
  \item Implemented a secondary indexing scheme on Apache Cassandra and a high throughput message ingestion service using Apache Thrift.
  \item Integrated Apache Hive to a cloud based multi‐tenanted environment including source level changes within
Hive to make it multi‐tenant aware.
\end{itemize}}

%------------------------------------------------

\NewEntry{2008, 2009}{Student Developer, \textsc{Google Summer of Code}}

\Description{\MarginText{GSoC} \begin{itemize}
  \item Apache Tomcat : Improved Tomcat JMX infrastructure making it possible to fully configure a Tomcat instance over JMX.
  \item Apache ODE : Integrated ODE based BPEL workflow support to BPELUnit. BPELUnit is an Eclipse based unit testing framework for BPEL processes.
\end{itemize}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Publications}\vspace{1em}

% \NewEntry{2017}{Publication Title}

\Description{\MarginText{PLDI'17 \\14.6\%}\textit{\textbf{Instruction Punning: Lightweight Instrumentation for x86-64}}, \\ \textbf{Buddhika Chamith},
Bo Joel Svensson, Luke Dalessandro, Ryan Newton}

\Description{\MarginText{ECOOP'17}\textit{\textbf{Compiling tree transforms to operate on packed representations}}, \\ Micheal Vollmer, Sarah Spall, \textbf{Buddhika Chamith}, Laith Sakka, Milind Kulkarni, Sam Tobin-Hochstadt, Ryan Newton}

\Description{\MarginText{PLDI'16 \\16\%}\textit{\textbf{Living on the edge: Rapid-toggling probes with cross modification on x86}}, \textbf{Buddhika Chamith},
Bo Joel Svensson, Luke Dalessandro, Ryan Newton}

\Description{\MarginText{LCPC'15}\textit{\textbf{Concurrent Cilk: Lazy Promotion from Tasks to Threads in C/C++}}, \\ Christopher Zakian,
Timothy Zakian, Abhishek Kulkarni, \textbf{Buddhika Chamith}, Ryan Newton}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE 
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Teaching Experience}\vspace{1em}

\Description{\MarginText{2013 Fall}Teaching Assistant for Introduction to Algorithms Graduate course.}
\Description{\MarginText{2017 Fall}Teaching Assistant for Programming Language Implementation Graduate course.}

%----------------------------------------------------------------------------------------
%	PROJECTS 
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Projects (Reverse Chronological)}\vspace{1em}

\Description{\MarginText{Kisseru}A Python library for scripting scientific dataflows.
{\href{https://github.com/chamibuddhika/kisseru/}{Github}}}
\Description{\MarginText{Liteprof}A lightweight binary instrumentation framework for x86-64.}
\Description{\MarginText{Haberno CNC/HPX}Integrated HPX distributed task execution enviornment as a CNC backend target. {\href{http://homes.soic.indiana.edu/budkahaw/CNC_HPX_PRINTED_SC15.pdf}{Poster}}}
\Description{\MarginText{Concurrent Cilk}A research prototype based on Intel Cilk with better support for blocking concurrency by promoting blocking lightweight threads to full OS threads.}
\Description{\MarginText{WSO2 Data Analytics Server}A data analytics and monitoring solution for enterprise middleware infrastructures. Contributed to the data analytics layer by integrating various big data solutions to the product.}
\Description{\MarginText{DSync}A distributed synchronization library based on Apache Zookeeper. {\href{https://chamibuddhika.wordpress.com/2011/08/29/dsync-a-distributed-synchronization-and-coordination-library/}{Blog}}}
\Description{\MarginText{Apache Tomcat}Improving Tomcat JMX infrastructure. {\href{https://blogs.apache.org/tomcat/entry/tomcat_7_trunk_and_jmx}{Blog}}}
\Description{\MarginText{BPELUnit}BPELUnit is a unit testing framework for BPEL processes. Integrated Apache ODE as a runtime backend for the BPELUnit Eclipse plugin (tutorials at {\href{http://www.se.uni-hannover.de/pages/en:tutorials_bpelunit_coverage_part_1}{[1]}} \& {\href{http://www.se.uni-hannover.de/pages/en:tutorials_bpelunit_coverage_part_2}{[2]}}).}


%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PROFICIENCIES 
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Proficiencies}\vspace{1em}

\Description{\MarginText{Programming Languages}C, C++, Java, Python, x86 Assembly, Racket, Haskell}

\vspace{1em}

\Description{\MarginText{Technologies}SOAP web services, REST, OSGi, 
Experience with some of the Apache Big Data stack including Hadoop, Hive, Cassandra, Thrift, Zookeeper}

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Professional Proficiency}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Sinhala}}\ \ $\cdotp$\ \ \ Native} 

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
